Report and Figures

### 2016-12-15 figs.Rmd
figures redone after bugfix in clustering

cluster_map('Detroit', 'Detroit', nclusters = 6)

@@

```{r}
make_cluster_groups('Detroit', 6) %>% 
	mutate(race = factor(race, levels = c('Other', 'Asian', 'Hispanic', 'Black', 'White'))) %>% 
  group_by(cluster) %>% 
  mutate(alpha = p / sum(p),
         total = sum(p)) %>% 
	ggplot(aes(y = race, x = cluster, fill = cluster)) + 
  scale_fill_brewer(palette = 'Set3', name = NULL, guide = 'none', labels = LETTERS[1:nclusters]) + 
	geom_tile(color = 'black',  aes(alpha = alpha), size = 1) + 
	geom_text(aes(
		label = ifelse(p < 0.005, "", 100 * round(p,2))), size = 8) + 
  scale_alpha_continuous(guide = 'none', limits = c(0, .3)) + 
	theme_minimal() + 
	theme(
	  text=element_text(size=25),
		  axis.ticks.x = element_blank(),
		  axis.title = element_blank(),
		  legend.position="bottom",
		  legend.title = element_blank(),
		  line = element_blank())

@@

```{r}
city <- 'Detroit'
print(city)
nclusters <- 1:6
g <- prominence_map(city, races)

@@

labels <- data_frame(label = c('A', 'B', 'C', 'D', 'E', 'F'),
                     long   = c(-83.35, -83.1558, -83.164, -82.905, -83.055, -83.1258),
                     lat  = c(42.37, 42.39, 42.28, 42.4, 42.4, 42.3214))

@@

@@

make_cluster_groups('Detroit', 6) %>% 
	mutate(race = factor(race, levels = c('Asian', 'Other', 'Hispanic', 'Black', 'White'))) %>% 
  group_by(cluster) %>% 
  mutate(alpha = p / sum(p),
         total = sum(p)) %>% 
	ggplot(aes(y = race, x = cluster, fill = race)) + 
  scale_fill_manual(values = c(pal[1], pal[4], pal[3], pal[2], pal[5]), name = NULL, guide = 'none', labels = LETTERS[1:nclusters]) + 
	geom_tile(color = 'black',  aes(alpha = alpha), size = 1) + 
	geom_text(aes(
		label = ifelse(p < 0.005, "", 100 * round(p,2))), size = 8) + 
  scale_alpha_continuous(guide = 'none', limits = c(0, 1)) + 
	theme_minimal() + 
	theme(
	  text=element_text(size=25),
		  axis.ticks.x = element_blank(),
		  axis.title = element_blank(),
		  legend.position="bottom",
		  legend.title = element_blank(),
		  line = element_blank())

>>>>

cluster_map('Detroit', 'Detroit', nclusters = 5)

@@

```{r}
make_cluster_groups('Detroit', 5) %>% 
	mutate(race = factor(race, levels = c('Other', 'Asian', 'Hispanic', 'Black', 'White'))) %>% 
  group_by(cluster) %>% 
  mutate(alpha = p / sum(p),
         total = sum(p)) %>% 
	ggplot(aes(y = race, x = cluster, fill = cluster)) + 
  scale_fill_brewer(palette = 'Set3', name = NULL, guide = 'none', labels = LETTERS[1:nclusters]) + 
	geom_tile(color = 'black',  aes(alpha = alpha), size = 1) + 
	geom_text(aes(
		label = ifelse(p < 0.005, "", 100 * round(p,2))), size = 8) + 
  scale_alpha_continuous(guide = 'none', limits = c(0, .3)) + 
	theme_minimal() + 
	theme(
	  text=element_text(size=25),
		  axis.ticks.x = element_blank(),
		  axis.title = element_blank(),
		  legend.position="bottom",
		  legend.title = element_blank(),
		  line = element_blank())

@@

```{r}
city <- 'Detroit'
print(city)
nclusters <- 1:5
g <- prominence_map(city, races)

@@

labels <- data_frame(label = c('A', 'B',  'E', 'C', 'D'),
                     long   = c(-83.35, -83.1568, -83.132, -82.905, -83.055),
                     lat  = c(42.37, 42.39, 42.32, 42.4, 42.4))

@@

  nclusters <- 1:5
  g <- g %>% cluster_map(city, races, nclusters)

@@

make_cluster_groups('Detroit', 5) %>% 
	mutate(race = factor(race, levels = c('Asian', 'Other', 'Hispanic', 'Black', 'White'))) %>% 
  group_by(cluster) %>% 
  mutate(alpha = p / sum(p),
         total = sum(p)) %>% 
	ggplot(aes(y = race, x = cluster, fill = race)) + 
  scale_fill_manual(values = c(pal[1], pal[4], pal[3], pal[2], pal[5]), name = NULL, guide = 'none', labels = LETTERS[1:nclusters]) + 
	geom_tile(color = 'black',  aes(alpha = alpha), size = 1) + 
	geom_text(aes(
		label = ifelse(p < 0.005, "", 100 * round(p,2))), size = 8) + 
  scale_alpha_continuous(guide = 'none', limits = c(0, 1)) + 
	theme_minimal() + 
	theme(
	  text=element_text(size=25),
		  axis.ticks.x = element_blank(),
		  axis.title = element_blank(),
		  legend.position="bottom",
		  legend.title = element_blank(),
		  line = element_blank())
